\chapter{Background}
% SE PÅ SamuelsenS MASTEROPPGAVE FOR INSPIRASJON (TROR HAN CLUSTERA OG KLASSIFISERTE HOVEDKONSEPTENE HAN BYGDE PÅ).

\gjor{Skriv opp bulletpoints fra mulige inspirasjoner og referanser her. "Write a few lines summarising relevant articles one comes across (which one is likely to refer to in the final report)" - Jims master-skrivingsdokument)}

\lab{Fra Essay-kommentarer} {
	\inkl {
		Often times, scientists have drawn inspiration from various scientific fields -- particularly different fields from ones own -- into their own field, for various reasons. Indeed, the translated concepts (from the one domain to the other) will most likely be accompanied with brand new ways to think about ones own domain, as well as other domains again interacting with it (hence having a real opportunity to start a "domino"-like chain-reaction of new ways to think about things emerging). These new ways to think about things (often in ones own domain) -- apart from being interesting and intriguing -- might be useful, both for ones own field but also for other fields again (especially if thinking long term). For example in the Multi-Agent Systems (MAS) field, it has been a common practice to study complex biological systems in nature, in order to translate these mechanisms into the technology- and engineering-domain (be it the \textit{Ant Colony(?)}, or \textit{Beeclust(?)}). Such bio-inspired algorithms have been -- \textit{and still are(?)} -- some of the most widely used optimization algorithms throughout history.
	}
	
	\inkl {
		(Fra Essay om 'path planning', 'EA's og 'multi-objective optimization'. Definitivt ikke kopier, men skriv om isåfall): "This essay attempts to give an overview over the fields of path-planning, evolutionary algorithms and multi-objective optimization, including pointers to recent work in these fields, especially where they intersect. In tradition with other literature relating to evolutionary algorithms, algorithms which are not population-based or otherwise based on principles similar to evolutionary algorithms are called ’classical’ to separate them from evolutionary variants."
	}
}

\tcol[gray]{\section{Nymoen et al. sin Firefly-Synkronisering:}}
	\inkl{
		\nl Nymoen et al. \cite{nymoen_synch} showed how one can, by endowing musical agents with self-awareness capabilities, achieve \textit{harmonic synchrony} of phases and frequencies in pulse-coupled oscillators.
		
		\sep
		
		% Recall of talk with Sigmund at the kitchen in M9
		\input{Assets/Presentations/sigmund_kitchen_recall.tex}
		
		\sep
		
		% (Ish) Recall of talk with Kjersti at home in the livingroom (when she came with Lucky)
		\input{Assets/Presentations/kjersti_livingroom_recall.tex}
	}

\section{Oscillators and Oscillator-Synchronization}

	\gjor{Beskrive dette så godt at jeg kan snakke fritt om oscillatorers \textbf{faser} og \textbf{frekvenser} senere (i Implementation f.eks.), spesielt i tilfelle noen ikke har vært borti det før, eller tatt et Signalbehandlings-kurs}
	
	\gjor{Skill på Pulse-coupled Oscillators, og Phase-coupled Oscillators}
	
	Much of the terminology from \cite{nymoen_synch} is used here. An oscillator $i$ is characterized by its \textit{phase} $\phi_i(t)$, which is initialized to 0 and evolves towards 1 at a rate of $\frac{d \phi_i(t)}{d t}$ — which is also called the \textit{frequency} of the oscillator.
	
	\subsection{Phase-adjustment}
				
	(If relevant and wanted) previous approaches to Phase-synchronization in oscillators (pulse- and/or phase-coupled).
		
	\subsection{Frequency-adjustment}
	
	(If relevant and wanted) previous approaches to Frequency-synchronization in oscillators (pulse- and/or phase-coupled) \tcol{cite(fixed\_freqs, fixed\_range\_freqs)} where the oscillators's frequencies are either equal and fixed, or where frequencies are bound to initialize and stay within a fixed interval/range.